Robust Bayesian Analysis of Causal Inference Problems

### 2024-03-21 JASA-template.tex
Comment.
Comments and some edits.

Let an observational study on $n$ individuals give us the outcomes $Y\coloneqq(Y_1, \dots, Y_n)$ along with 
corresponding treatment indicators $T\coloneqq(T_1, \dots, T_n)$. Then the
treatment 
effect in the population is given by the expectation of the difference
in outcomes between the treatment and controls:
%%% MT to TB: I don't understand this equation; since Y and T are vectors, is \delta simply \delta_1,\dots,\delta_n? I think something else is meant? or remove this equation?
\begin{align}
	\delta = \mathbb{E}(Y\mid T =1) - \mathbb{E}(Y\mid T=0).
\end{align}
Similarly, the individual causal
effect of treatment $T_i$ on outcome $Y_i$ is given by:
\begin{align}
	\delta_i \coloneqq \mathbb{E}(Y_i\mid T_i=1) - \mathbb{E}(Y_i\mid T_i=0).
\end{align}
That is, we are interested in the difference between the outcomes when the $i$-th subject receives
the treatment and when 
%$i$-th subject 
it remains as a control.

In theory, both of these quantities exist.
However, we cannot observe $\mathbb{E}(Y_i\mid T_i=1)$ and $\mathbb{E}(Y_i\mid T_i=0)$
the average causal effect of the treatment $T$ by calculating the averaged
outcome of all the subjects that received the treatment and
all the subjects that remained as control:
\begin{align}
	\hat{\delta} \coloneqq 
	\frac{\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=1) - 
		\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=0)}{n}.
\end{align}
However, this relies on an important assumption that the treatment effect
on the $i$-th subject given that they received the treatment is the same as the (counterfactual) treatment effect when they remain as control \cite{winship99}.

>>>>

Let an observational study on $n$ individuals give us the outcomes $Y\coloneqq(Y_1, \dots, Y_n)$ along with 
corresponding treatment indicators $T\coloneqq(T_1, \dots, T_n)$. Then the
treatment 
effect in the population is given by the expectation of the difference
in outcomes between the treatment and controls:
%%% MT to TB: I don't understand this equation; since Y and T are vectors, is \delta simply \delta_1,\dots,\delta_n? I think something else is meant? or remove this equation?
\begin{align}
	\delta = \mathbb{E}(Y\mid T =1) - \mathbb{E}(Y\mid T=0).
\end{align}
Similarly, the individual causal
effect of treatment $T_i$ on outcome $Y_i$ is given by:
\begin{align}
	\delta_i \coloneqq \mathbb{E}(Y_i\mid T_i=1) - \mathbb{E}(Y_i\mid T_i=0).
\end{align}
%%% MT to TB: are we interested in predicting the effect on an individual that is not yet observed, i.e. say $\delta_{n+1}$?
That is, we are interested in the difference between the outcomes when the $i$-th subject receives
the treatment and when 
%$i$-th subject 
it remains as a control.

In theory, both $\mathbb{E}(Y_i\mid T_i=1)$ and $\mathbb{E}(Y_i\mid T_i=0)$ exist.
However, we cannot observe them simultaneously, since we cannot `treat' and `not treat' the same individual at the same time.
What we can observe is the average causal effect of the treatment,
by calculating the averaged
outcome of all the subjects that received the treatment and
all the subjects that remained as control:
\begin{align}
  \hat{\delta} \coloneqq 
  \frac{\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=1)-\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=0)}{n}.
\end{align}
However, this relies on an important assumption that the treatment effect
on the $i$-th subject given that they received the treatment is the same as the (counterfactual) treatment effect when they remain as control \cite{winship99}.
